 

### 2018-09-24 Manuscript/SupplementaryMaterial.tex
Supplementary material

---
title: " "
author: |
bibliography: CircularData.bib
csl: apa.csl
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    latex_engine: pdflatex
    number_sections: no
fontsize: 12pt
geometry: margin=1in
header-includes:
  - \usepackage{multirow}
  - \usepackage{appendix}
  - \usepackage{color}
  - \usepackage{hyperref}
  - \usepackage{subcaption}
  - \setlength\parindent{24pt}
  - \usepackage{setspace}\doublespacing
documentclass: article
pandoc_args: --natbib
---

@@

In this Supplementary Material we outline the MCMC procedures to fit the cylindrical regression models. R-code for the MCMC sampler and the analysis of the teacher data can be found here: \url{https://github.com/joliencremers/CylindricalComparisonCircumplex}. Note that the dimensions of the objects (design matrices, mean vectors, etc.) are those that were used in the analysis of the teacher data where we have 1 circular outcome, 1 linear outcome and estimate an intercept and regression coefficient for the covariate self-efficacy. Note that for the regression of the linear component in the CL-PN and CL-GPN models we also have the sine and cosine of the circular outcome in the regression equation, this makes the vector with regression coefficients, $\boldsymbol{\gamma}$, four-dimensional.

@@

\newpage
\subsection{Bayesian Model and MCMC procedure for the modified CL-GPN model}\label{A2}

@@

\newpage
\subsection{Bayesian Model and MCMC procedure for the modified GPN-SSN model}\label{A3}

@@

>>>>

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}

  \title{}
    \pretitle{\vspace{\droptitle}}
  \posttitle{}
    \author{}
    \preauthor{}\postauthor{}
    \date{}
    \predate{}\postdate{}

\usepackage{multirow}
\usepackage{appendix}
\usepackage{color}
\usepackage{hyperref}
\usepackage{subcaption}
\setlength\parindent{24pt}
\usepackage{setspace}\doublespacing

\begin{document}

@@

In this Supplementary Material we outline the MCMC procedures to fit the
cylindrical regression models. R-code for the MCMC sampler and the
analysis of the teacher data can be found here:
\url{https://github.com/joliencremers/CylindricalComparisonCircumplex}.
Note that the dimensions of the objects (design matrices, mean vectors,
etc.) are those that were used in the analysis of the teacher data where
we have 1 circular outcome, 1 linear outcome and estimate an intercept
and regression coefficient for the covariate self-efficacy. Note that
for the regression of the linear component in the CL-PN and CL-GPN
models we also have the sine and cosine of the circular outcome in the
regression equation, this makes the vector with regression coefficients,
\(\boldsymbol{\gamma}\), four-dimensional.

@@

\newpage

\subsection{Bayesian Model and MCMC procedure for the modified CL-GPN model}\label{A2}

@@

\newpage

\subsection{Bayesian Model and MCMC procedure for the modified GPN-SSN model}\label{A3}

@@

\end{document}
